\tocless\section{Tags of Solutions for Algorithms}
\label{sec:algo_tag}
\addcontentsline{toc}{section}{\protect\numberline{}Tags of Solutions for Algorithms}

\subsection*{Binary Tree}
\begin{flushleft}
    \hyperref[algo:617]{617. Merge Two Binary Trees}

    \hyperref[algo:654]{654. Maximum Binary Tree}

    \hyperref[algo:669]{669. Trim a Binary Search Tree}

    \hyperref[algo:814]{814. Binary Tree Pruning}
\end{flushleft}

\subsection*{Bitwise Operation}
\begin{flushleft}
    \hyperref[algo:338]{338. Counting Bits}

    \hyperref[algo:461]{461. Hamming Distance}

    \hyperref[algo:476]{476. Number Complement}
\end{flushleft}

\subsection*{Cryptology}
\begin{flushleft}
    \hyperref[algo:535]{535. Encode and Decode TinyURL}
\end{flushleft}

\subsection*{Graph}
\begin{flushleft}
    \hyperref[algo:797]{797. All Paths From Source to Target}
\end{flushleft}

\subsection*{Hash Table}
\begin{flushleft}
    \hyperref[algo:575]{575. Distribute Candies}

    \hyperref[algo:771]{771. Jewels and Stones}

    \hyperref[algo:791]{791. Custom Sort String}

    \hyperref[algo:804]{804. Unique Morse Code Words}

    \hyperref[algo:811]{811. Subdomain Visit Count}
\end{flushleft}

\subsection*{Math}
\begin{flushleft}
    \hyperref[algo:537]{537. Complex Number Multiplication}

    \hyperref[algo:657]{657. Judge Route Circle}

    \hyperref[algo:728]{728. Self Dividing Numbers}
\end{flushleft}

\subsection*{Recursive Algorithm}
\begin{flushleft}
    \hyperref[algo:617]{617. Merge Two Binary Trees}
    
    \hyperref[algo:669]{669. Trim a Binary Search Tree}

    \hyperref[algo:814]{814. Binary Tree Pruning}
\end{flushleft}

\subsection*{Sort}
\begin{flushleft}
    \hyperref[algo:791]{791. Custom Sort String}
\end{flushleft}

\subsection*{Stack \& Heap}
\begin{flushleft}
    \hyperref[algo:682]{682. Baseball Game}
\end{flushleft}

\subsection*{String \& Array}
\begin{flushleft}
    \hyperref[algo:344]{344. Reverse String}

    \hyperref[algo:419]{419. Battleships in a Board}
    
    \hyperref[algo:463]{463. Island Perimeter}

    \hyperref[algo:500]{500. Keyboard Row}

    \hyperref[algo:537]{537. Complex Number Multiplication}

    \hyperref[algo:557]{557. Reverse Words in a String III}

    \hyperref[algo:561]{561. Array Partition I}

    \hyperref[algo:575]{575. Distribute Candies}

    \hyperref[algo:763]{763. Partition Labels}

    \hyperref[algo:791]{791. Custom Sort String}

    \hyperref[algo:806]{806. Number of Lines To Write String}

    \hyperref[algo:821]{821. Shortest Distance to a Character}
    
    \hyperref[algo:868]{868. Binary Gap}

    \hyperref[algo:1480]{1480. Running Sum of 1d Array}
\end{flushleft}
