\section*{535. Encode and Decode TinyURL}
\label{algo:535}

\subsection*{Difficulty}
Medium

\subsection*{Tags}
Cryptology

\subsection*{Description}
TinyURL is a URL shortening service where you enter a URL such as \inlinecode{https://leetcode.com/problems/design-tinyurl} and it returns a short URL such as \inlinecode{http://tinyurl.com/4e9iAk}.

Design the \inlinecode{encode} and \inlinecode{decode} methods for the TinyURL service. There is no restriction on how your encode/decode algorithm should work. You just need to ensure that a URL can be encoded to a tiny URL and the tiny URL can be decoded to the original URL.

\subsection*{Analysis}
This is an open problem where numerous solutions can be applied. We can even keep the original url as encode and decode, although it is meaningless.

We should to pay attention to these limitations:
\begin{itemize}
	\item Correctness: We must make sure that the decoded url is the same as the original url.
	\item Uniqueness: Each url must have an unique encoded url, and an encoded url must be decoded to a single url.
	\item Simplicity: The aim to encode a url is to make it easy to share or write, so we need to make the encoded url as simple as possible.
\end{itemize}

We can use current popular encode/decode algorithms such as \inlinecode{AES}, \inlinecode{DES}, but in this problem, we just design a simpler algorithm to encode and decode a url.
\begin{minted}[
	framesep=2mm,
	baselinestretch=1.2,
	bgcolor=codebackground,
	fontsize=\footnotesize]{matlab}
function encode(url)
    return hex(current number of urls in hash table)
end

function decode(encoded_url)
    return (hash table).find(encoded_url)
end
\end{minted}

\newpage

\subsection*{Solution}
\subsubsection*{C++}
\begin{minted}[framesep=2mm,
baselinestretch=1.2,
bgcolor=codebackground,
fontsize=\footnotesize,
linenos]{c++}
typedef unordered_map<string, string> Urlmap;

class Solution {
public:

    Urlmap urlmap;
    
    // Encodes a URL to a shortened URL.
    string encode(string longUrl) {
        size_t size = urlmap.size();
        stringstream encoded;
        encoded << hex << size;
        string encoded_url = encoded.str();
        urlmap.insert(make_pair(encoded_url, longUrl));
        return encoded_url;
    }
    
    // Decodes a shortened URL to its original URL.
    string decode(string shortUrl) {
    Urlmap::iterator it = urlmap.find(shortUrl);
    if (it == urlmap.end()) return NULL;
        return it->second;
    }
};
\end{minted}

\newpage
