\tocless\section{791. Custom Sort String}
\label{algo:791}

\subsection*{Difficulty}
Medium

\subsection*{Tags}
Hash Table, Sort, String \& Array

\subsection*{Description}
\inlinecode{S} and \inlinecode{T} are strings composed of lowercase letters. In \inlinecode{S}, no letter occurs more than once.

\inlinecode{S} was sorted in some custom order previously. We want to permute the characters of \inlinecode{T} so that they match the order that \inlinecode{S} was sorted. More specifically, if \inlinecode{x} occurs before \inlinecode{y} in \inlinecode{S}, then \inlinecode{x} should occur before \inlinecode{y} in the returned string.

Return any permutation of \inlinecode{T} (as a string) that satisfies this property.

\begin{example}
\begin{multilinecode}
Input:
S = "cba"
T = "abcd"
Output:
"cbad"
Explanation: 
"a", "b", "c" appear in S, so the order of "a", "b", "c" should be "c", "b", and "a". 
Since "d" does not appear in S, it can be at any position in T. "dcba", "cdba", "cbda" are also valid outputs.
\end{multilinecode}
\end{example}

\textbf{Note}
\begin{itemize}
    \item \inlinecode{S} has length at most \inlinecode{26}, and no character is repeated in \inlinecode{S}.
    \item \inlinecode{T} has length at most \inlinecode{200}.
    \item \inlinecode{S} and \inlinecode{T} consist of lowercase letters only.
\end{itemize}

\subsection*{Analysis}
You could easily think up that you can customize the compare function of quick sort according to \inlinecode{S}. However, the time complexity will be $\mathcal{O}(n\log{n})$ assuming the length of \inlinecode{T} is $n$.

We can use a linear method to calculate the count of each letter in \inlinecode{T} and reconstruct \inlinecode{T} according the appearance order of letters in \inlinecode{S}. By the way, we can use another array to store letters which are not appear in \inlinecode{S}.
\begin{itemize}
    \item Time complexity: $\mathcal{O}(n)$ (because the length of \inlinecode{S} will not exceed \inlinecode{26})
    \item Space complexity: $\mathcal{O}(n)$
\end{itemize}

\subsection*{Solution}
\subsubsection{C}
\begin{minted}[framesep=2mm,
baselinestretch=1.2,
bgcolor=codebackground,
fontsize=\footnotesize,
breaklines,
linenos]{c}
char* customSortString(char* S, char* T) {
    int appearance[26] = { 0 };
    int counts[26] = { 0 };
    char extra_letters[200];
    int extra_letters_count = 0;
    char c;
    // find which letters appear in S
    for (int i = 0; (c = S[i]) != '\0'; ++i) {
        appearance[c - 'a'] = 1;
    }
    // count the frequency of T
    for (int i = 0; (c = T[i]) != '\0'; ++i) {
        if (appearance[c - 'a'] == 0) extra_letters[extra_letters_count++] = c;
        else ++counts[c - 'a'];
    }
    int len = 0;
    // reconstruct T according to the order in S
    for (int i = 0; (c = S[i]) != '\0'; ++i) {
        int count = counts[c - 'a'];
        for (int k = 0; k < count; ++k) {
            T[len++] = c;
        }
    }
    // append the letters not appeared in S
    for (int i = 0; i < extra_letters_count; ++i) {
        T[len++] = extra_letters[i];
    }
    return T;
}
\end{minted}

\newpage

